---
title: "Snakes and Ladders"
author: "Matt"
date: "2/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document contains student solutions to the snakes and ladders problem. Students will add to this file using the outline below. Write your name (using three hashtags), then below create an R code block and insert your code. Save the .rmd file, then knit the document to update the html output. Then submit a pull request to merge your changes to the main repository.

### Jeff Kravitz

```{r}
move <- 0
count <- replicate(1000, 0)
game_grid <- data.frame(c(3,6,9,10,14,19,22,24),c(11,17,18,12,4,8,20,16))
for (i in 1:1000) {
  spot <- 1
  while (spot <= 25) {
  move <- sample(1:6, 1)
  spot <- spot + move
  for (i in 1:8) {
    if (spot == game_grid[i,1]) {
      spot <- game_grid[i,2]
    }
  }
  count[i] = count[i] + 1
  }
}
avg_moves <- mean(count)
print(avg_moves)
```

### Norander Wilson 
I tried, however I was unable to complete
this what i have done. 
---
title: "Snakes"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
n=100


M=matrix(0,n+1,n+1+6)
rownames(M)=0:n
colnames(M)=0:(n+6)


for(i in 1:6){
  diag(M[,(i+1):(i+1+n)])=1/6
}


for(i in 96:100) {
  for(c in 102:107) {
    idx = 101 - (c - 101)  
    M[i, idx] = M[i, idx] + M[i, c]
  }  
}

M=M[,1:(n+1)]

# add in the snakes and ladders
starting = c(4,9,17,20,28,40,51,54,62,64,63,71,93,95,92)
ending   = c(14,31,7,38,84,59,67,34,19,60,81,91,73,75,78)


M <- 1:106
  names(M) <- as.character(1:106)
  M[transitions[,1]] <- transitions[,2]

  lastpos <- 0
  curpos <- history <- NULL
  while(all(curpos < 100)) {
    curpos <- lastpos + sample(1:6, nplayers, repl=TRUE)
    curpos <- transmat[curpos]
    if(any(curpos > 100)) curpos[curpos > 100] <- lastpos[curpos > 100]

    lastpos <- curpos
    history <- rbind(history, curpos)
  }

```
